---
title: "OSA Tutorial"
author: "Andrea Havron"
date: "2025-06-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## One-step ahead residuals introduction

Outline of methods and assumptions

## Methods
Examples will reply on two models from the [TMB example suite](https://github.com/kaskr/adcomp/tree/master/TMB/inst/examples):

* [simple.cpp](https://github.com/kaskr/adcomp/blob/master/TMB/inst/examples/simple.cpp): normal linear mixed model
* [arxar1.cpp](https://github.com/kaskr/adcomp/blob/master/TMB/inst/examples/ar1xar1.cpp): generalized linear mixed model with separable covariance on lattice with AR1 structure in each direction

Examples can be run in R using: `TMB::runExample(name = "simple")` and `TMB::runExample(name = "ar1xar1")`

### Assumption #1: Data and random effects are approximately normal

```{r run-simple, echo = FALSE}
path <- here::here()
TMB::runExample(name = "randomwalkvalidation", exfolder = paste0(path,"/inst/examples"))
```

```{r plot-simple}
#Plot data: 
plot(1:length(Y), Y)
```
#### Full Guassian
```{r run-fg-correct, echo = FALSE}
#Correct Model
osa <- TMB::oneStepPredict(obj1, observation.name = "y", method = "fullGaussian")
```

```{r plot-fg-correct}
qqnorm(osa$residual)
abline(0,1)
```

```{r run-fg-misp, echo = FALSE}
#Mis-specified Model
osa <- TMB::oneStepPredict(obj0, observation.name = "y", method = "fullGaussian")
```

```{r plot-fg-misp}
qqnorm(osa$residual)
abline(0,1)
```

#### one-step Guassian
```{r run-osg, echo = FALSE}
osa <- TMB::oneStepPredict(obj1, observation.name = "y", data.term.indicator = "keep", 
                      method = "oneStepGaussian")
```

```{r plot-osg}
qqnorm(osa$residual)
abline(0,1)
```

### Assumption #2: Data are not approximately normal but have a defined cdf
```{r run-ar1xar1, echo = FALSE}
TMB::runExample(name = "ar1xar1")
```

```{r plor-ar1xar1}
#Plot data: 
ggplot2::ggplot(d, ggplot2::aes(x,y,fill = N)) + ggplot2::geom_raster()
```

Data are discrete, so need to set discrete = TRUE

#### cdf
```{r run-cdf, echo = FALSE}
osa <- TMB::oneStepPredict(obj, observation.name = "N", data.term.indicator = "keep",
                      method = "cdf", discrete = TRUE)
```

```{r plot-cdf}
qqnorm(osa$residual);abline(0,1)
```

### Assumption #3: Data are not approximately normal and do not have a defined cdf
```{r run-gen, echo = FALSE}
osa <- TMB::oneStepPredict(obj, observation.name = "N", data.term.indicator = "keep",
                      method = "oneStepGeneric", discrete = TRUE)
```

```{r plot-gen}
qqnorm(osa$residual);abline(0,1)
```
