---
title: Results - KS Test
output: html_document
---

<br>

```{r, include = FALSE, warning = FALSE, message = FALSE }
source("../R/update-results.R")
#Set update = TRUE to update results from source code
update_results(update = FALSE)
source("../results/results-setup.R")
```

\clearpage
\newpage
# Spatial Covariance Structure
## Linear Mixed Model
### Theoretical Residuals

#### Kolmogorov-Smirnov Test

```{r, spatial-results-LMM-true-ks, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Gamma (C), Mis-specified Random Effect (D)."}

res.methods <- c(
   'full Gaussian',
   'one-step Gaussian',
   'one-step Generic',
   'cdf',
   'MCMC',
   'Pearson',
   "Unconditional ecdf, Not Rotated", 
   "Conditional ecdf, Not Rotated",
   "Unconditional ecdf, Rotated", 
   "Conditional ecdf, Rotated"
)

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "GOF.ks",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Anderson-Darling Test

```{r, spatial-results-LMM-true-ad, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "GOF.ad",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Spatial Autocorrelation Test

```{r, spatial-results-LMM-true-sp, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I Spatial Correlation Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "SAC",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```


<br>

### Estimated Residuals

#### Kolmogorov-Smirnov

```{r, spatial-results-LMM-est-ks, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "GOF.ks",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

<br>

#### Anderson-Darling Test

```{r, spatial-results-LMM-est-ad, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Lognormal (C),Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "GOF.ad",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Spatial Autocorrelation Test

```{r, spatial-results-LMM-est-sp, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I spatial autocorrelation test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Normal data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "LMM", 
                       test_ = "SAC",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "ln-error", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Lognormal Error",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```


<br>

## Generalized Linear Mixed Model
### Theoretical Residuals

#### Kolmogorov-Smirnov Test

```{r, spatial-results-GLMM-true-ks, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "GOF.ks",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Anderson-Darling Test

```{r, spatial-results-GLMM-true-ad, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "GOF.ad",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
           levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Spatial Autocorrelation Test

```{r, spatial-results-GLMM-true-sp, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I Spatial Correlation Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C),  Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "SAC",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
           levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

<br>

### Estimated Residuals

#### Kolmogorov-Smirnov

```{r, spatial-results-GLMM-est-ks, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "GOF.ks",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

<br>

#### Anderson-Darling Test

```{r, spatial-results-GLMM-est-ad, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "GOF.ad",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Spatial Autocorrelation Test

```{r, spatial-results-GLMM-est-sp, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I spatial autocorrelation test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Gamma data fit to Lognormal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "spatial", 
                       type = "GLMM", 
                       test_ = "SAC",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
          levels = c( "correct", 
                     "missre", 
                     "pois-zip", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: NB-Pois",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

