---
title: Results - KS Test
output: html_document
---

<br>

```{r, include = FALSE, warning = FALSE, message = FALSE }
source("../R/update-results.R")
#Set update = TRUE to update results from source code
update_results(update = FALSE)
source("../results/results-setup.R")
```

\clearpage
\newpage
# Phylogenetic Covariance Structure
## Linear Mixed Model
### Theoretical Residuals

#### Kolmogorov-Smirnov Test

```{r, phylo-results-LMM-true-ks, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal (C), Mis-specified Random Effect (D)."}

res.methods <- c(
   'full Gaussian',
   'one-step Gaussian',
   'one-step Generic',
   'one-step cdf',
   'MCMC',
   'Pearson',
   "Unconditional ecdf", 
   "Conditional ecdf"
)

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Kolmogorov- Smirnov",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Anderson-Darling Test

```{r, phylo-results-LMM-true-ad, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B),, Log-linked data fit to Normal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Anderson-Darling",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Phylogenetic Autocorrelation Test

```{r, phylo-results-LMM-true-sp, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I Phylogenetic Correlation Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Autocorrelation",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```


<br>

### Estimated Residuals

#### Kolmogorov-Smirnov

```{r, phylo-results-LMM-est-ks, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Kolmogorov- Smirnov",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Lilliefors

```{r, phylo-results-LMM-est-lf, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Lilliefors Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal  (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Lilliefors",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

<br>

#### Anderson-Darling Test

```{r, phylo-results-LMM-est-ad, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal (C),Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Anderson-Darling",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Phylogenetic Autocorrelation Test

```{r, phylo-results-LMM-est-sp, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I phylogenetic autocorrelation test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Log-linked data fit to Normal (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "LMM", 
                       test_ = "Autocorrelation",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "identity-log", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Misp. Link",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```


<br>

## Generalized Linear Mixed Model
### Theoretical Residuals

#### Kolmogorov-Smirnov Test

```{r, phylo-results-GLMM-true-ks, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Kolmogorov- Smirnov",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
        levels = c( "correct",
                     "missre", 
                     "misscov", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Anderson-Darling Test

```{r, phylo-results-GLMM-true-ad, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Anderson-Darling",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
           levels = c( "correct", 
                     "missre", 
                     "misscov", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

#### Phylogenetic Autocorrelation Test

```{r, phylo-results-GLMM-true-sp, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 10, fig.cap = "Generalized Linear Mixed Model. Distribution of theoretical p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I Phylogenetic Correlation Test for each method when true parameters are known. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C),  Mis-specified Random Effect (D)."}

pval.df <- filter.true(df = pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Autocorrelation",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
           levels = c( "correct", 
                     "missre", 
                     "misscov",
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, TRUE)
```

<br>

### Estimated Residuals

#### Kolmogorov-Smirnov

```{r, phylo-results-GLMM-est-ks, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Kolmogorov-Smirnov Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Kolmogorov- Smirnov",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "misscov", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Lilliefors

```{r, phylo-results-GLMM-est-lf, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Lilliefors Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Lilliefors",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "misscov", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

<br>

#### Anderson-Darling Test

```{r, phylo-results-GLMM-est-ad, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Anderson-Darling Test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Anderson-Darling",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
         levels = c( "correct", 
                     "missre", 
                     "misscov",
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

#### Phylogenetic Autocorrelation Test

```{r, phylo-results-GLMM-est-sp, echo = FALSE, message = FALSE, fig.height = 9, fig.cap = "Generalized Linear Mixed Model. Distribution of estimated p-values under the correct (A) and mis-specified (B-D) models evaluated under the Moran's I phylogenetic autocorrelation test for each method when parameters are estimated. Mis-specification are, from left to right: Missing Random Effect (B), Missing Covariate (C), Mis-specified Random Effect (D)."}

pval.df <- filter.est(pvals, 
                       mod = "phylo", 
                       type_ = "GLMM", 
                       test_ = "Autocorrelation",
                       res.methods)

pval.df$misp <- factor(pval.df$misp,
          levels = c( "correct", 
                     "missre", 
                     "misscov", 
                     "mispre"),
         labels = c("A: Correct",
                    "B: Miss RE",
                    "C: Miss Cov",
                    "D: Misp. RE" ))

plot.pval.hist(pval.df, FALSE)
```

